---
title: "p8105_hw3_js5165"
author: "Jingqi Song"
date: "October 13, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
```

## Problem 1

```{r Problem1}
library(p8105.datasets)
p1_brfss=brfss_smart2010 %>% 
  janitor::clean_names() %>%
  separate(locationdesc, into = c("state", "county"), sep = " - ") %>%
  filter(topic=='Overall Health')%>%
  mutate(response = forcats::fct_relevel(response, c("excellent", "very_good", "good", "fair", "poor"))) %>% 
  select(-locationabbr, year, state, county, response, everything())


#In 2002, which states were observed at 7 locations
p1_brfss%>%
  filter(year == 2002) %>% 
  group_by(state) %>% 
  summarize(count = n_distinct(county)) %>% 
  filter(count == 7)

#plot that shows the number of locations in each state from 2002 to 2010
p1_brfss%>%
  group_by(state, year) %>% 
  summarize(location_num = n_distinct(county)) %>% 
  ggplot(aes(x = year, y = location_num, color = state)) + 
  geom_point() + 
  geom_line(alpha = .5) +
    labs(
    title = "Number of locations" ,
    x = "Year" ,
    y = "Number"
    ) +
  theme(legend.position = "right")
  

#table for mean and standard deviation
p1_brfss_3 = p1_brfss %>%
  spread(key = response, value = data_value) %>% 
  janitor::clean_names() %>%
  filter( year == 2002 | year == 2006 | year == 2010) %>%   
  filter(state == "NY") %>% 
  group_by(state, county) %>% 
  summarize(avg_excellent = mean(excellent, na.rm = TRUE),sd_excellent = sd(excellent, na.rm = TRUE)) %>% 
  knitr::kable(digits = 2)
p1_brfss_3


#five-panel plot 
p1_average = p1_brfss %>%
  spread(key = response, value = data_value) %>% 
  janitor::clean_names() %>%
  select(year, state, county, excellent:poor) %>% 
  group_by(state, year) %>% 
  summarize(avg_excellent = mean(excellent, na.rm = TRUE), avg_very_good = mean(very_good, na.rm = TRUE), avg_good = mean(good, na.rm = TRUE), avg_fair = mean(fair, na.rm = TRUE), avg_poor = mean(poor, na.rm = TRUE)) %>% 
  gather(key = "avg_type", value = "avg_proportion", avg_excellent:avg_poor) %>%
  mutate(avg_type = forcats::fct_relevel(avg_type, c("avg_excellent", "avg_very_good", "avg_good", "avg_fair", "avg_poor")))

ggplot(p1_average, aes(x = year, y = avg_proportion, color = state)) + 
  geom_point() + 
  geom_line(alpha = .5) +
  facet_grid(~ avg_type) +
  labs(
    title = "State-Level Average Proportion",
    x = "Year",
    y = "Average proportion"
  ) + 
  theme(legend.position = "right", axis.text.x = element_text(angle = 40))
  
```

In 2002, Connecticut, Florida and North Carolina were observed at 7 locations.


## Problem 2

```{r Problem2}
p2_instacart = instacart

#which aisles are the most items ordered from
p2_instacart %>% 
  group_by(aisle) %>% 
  summarize(count = n()) %>% 
  arrange(-count)%>%
  head(5)

#plot that shows the number of items ordered in each aisle
p2_instacart %>% 
  group_by(aisle) %>% 
  summarize(count = n()) %>% 
  mutate(aisle = forcats::fct_reorder(aisle, count),
    aisle_grp = as.numeric(cut_number(count, 3))) %>% 
  ggplot(aes(x = aisle, y = count)) +
    geom_point() +
    facet_wrap(~ aisle_grp, nrow = 3, scales = "free") +
    theme(axis.text.x = element_text(size = 7, hjust = 1, angle = 40)) +
    labs(
      title = "Number of Items Ordered in Each Aisle",
      x = "Aisle Name",
      y = "Number of Items Ordered"
      )

# the most popular item in “baking ingredients”, “dog food care”, and “packaged vegetables fruits”
p2_instacart %>%  
  filter(aisle == 'baking ingredients' | aisle == 'dog food care' | aisle == 'packaged vegetables fruits') %>% 
  group_by(aisle, product_name) %>% 
  summarize(count = n()) %>% 
  group_by(aisle) %>% 
  filter(min_rank(desc(count))< 2) 

#table of the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered
p2_instacart %>%  
  filter(product_name == 'Pink Lady Apples' | product_name == 'Coffee Ice Cream') %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  spread(key = 'product_name', value = 'mean_hour') %>% 
  mutate(order_day = 'Monday',
         order_dow = weekdays(order_day, abbreviate) + order_dow) %>% 
  knitr::kable()

```

There are in all 134 aisles; fresh vegetables, fresh fruits, and packaged vegetable fruits are the most items ordered from.

The most popular item in baking ingredients, dog food care and packaged vegetables fruits are Light Brown Suger, Snack Sticks Chicken & Rice Recipe Dog Treats, and Organic Baby Spinach respectively.















